Small induced universal graphs

### 2021-08-24 paper/paper.tex
Add Chain Markov's lower bound

The values $f(4)$ and $f(5)$ are equal to a simple lower bound
given in a comment by ``bof'' on Mathematics Stack Exchange
\cite{math_se_question}: $f(k) \geq 2k$ if $k \geq 4$.  (For $k < 10$, this
bound improves upon Moon's lower bound.)  To briefly summarise the proof, if $k \leq 2k$
then $G$ must be a split graph (that is, a graph whose vertices can be
partitioned into a clique and an independent set); therefore, $G$ cannot
contain the cycle $C_4$ as an induced subgraph.  An example of an 8-vertex
induced universal graph for the family of 4-vertex graphs was given by ``Chain
Markov'' as a comment on the same question.

>>>>

The values $f(1)$, $f(2)$ and $f(3)$ are equal to to the simple lower bound $2k
- 1$ given in a question by ``Chain Markov'' on Mathematics Stack Exchange
\cite{math_se_question}.  The values $f(4)$ and $f(5)$ are equal to a lower
bound given in a comment by ``bof'' on that question: $f(k) \geq 2k$ if $k \geq
4$.  (For $k < 10$, this bound improves upon Moon's lower bound.)  To briefly
summarise the proof, if $k \leq 2k$ then $G$ must be a split graph (that is, a
graph whose vertices can be partitioned into a clique and an independent set);
therefore, $G$ cannot contain the cycle $C_4$ as an induced subgraph.  An
example of an 8-vertex induced universal graph for the family of 4-vertex
graphs was given by ``Chain Markov'' as a comment on the same question.
